\documentclass[11pt, letter]{article}
\usepackage{jk-vita}
\usepackage{enumitem}
\usepackage{fontawesome5}

\title{}
\name{Stefan D. McCabe}
\address{
    805 21\textsuperscript{st} Street \textsc{NW}\\
    Unit 201 \\
    Washington, DC 20052
}
\www{sdmccabe.com}
\email{stefan.mccabe@gwu.edu}
\twitter{mccabe\_s}
\tel{(571) 432-8219}
\subject{}
\hypersetup{xetex,
    colorlinks=true,
    urlcolor=ImperialBlue,
    citecolor=ImperialBlue,
}
\begin{document}

\maketitle

\section{employment}

%\textbf{Institute for Data, Democracy \& Politics, The George Washington University} \hfill 12/2022-- \\
\subsection{The George Washington University}

Postdoctoral Associate, Institute for Data, Democracy \& Politics \hfill 12/2022-- \\
Advisors: Matthew Hindman, Andrew Ifedapo Thompson
\vspace{2mm}

\subsection{Microsoft Research NYC} 
Research Intern \hfill 05/2020--09/2020 \\
Advisor: David Rothschild
\vspace{2mm}

%Research Intern, Microsoft Research NYC. Advisor: David Rothschild (Summer 2020)
\vspace{-1mm}

\section{education}
\subsection{Northeastern University, PhD in Network Science, 2022}
Dissertation: ``Essays on the Measurement of Online Behavior''

Committee: David Lazer (chair), Nick Beauchamp, Katherine Haenschen, Kevin Esterling

\subsection{George Mason University, MA in Computational Social Science, 2016}
Thesis: ``Communicating Sequential Agents: An Analysis of Concurrent Agent Scheduling''

Committee: Robert Axtell (chair), Andrew Crooks, Kenneth Comer
\subsection{George Mason University, BA in Government \& International Politics,
  2013}

\vspace{2mm}

\section{publications}
\vspace{1mm} {\footnotesize (\textdagger\, indicates joint first authorship)}
\subsection*{} % used for padding the preceding parenthetical

\subsection{2023}
\begin{hangparas}{.25in}{1}
Klein, Brennan,\textsuperscript{\textdagger} Timothy LaRock,\textsuperscript{\textdagger} \textbf{Stefan McCabe},\textsuperscript{\textdagger} Leo Torres,\textsuperscript{\textdagger} Lisa Friedland, Maciej Kos, Filippo Privitera, Brennan Lake, Moritz U. G. Kraemer, John S. Brownstein, Richard Gonzalez, David Lazer, Tina Eliassi-Rad, Samuel V. Scarpino, Alessandro Vespignani, and Matteo Chinazzi. Revise \& resubmit, \textit{PLOS Digital Health}. ``Reshaping a Nation: Mobility, Commuting, and Contact Patterns During the COVID-19 Outbreak.'' \href{https://covid19.gleamproject.org/mobility}{https://covid19.gleamproject.org/mobility} arXiv:\href{https://arxiv.org/abs/2212.08873}{2212.08873}\vspace{2mm}

Gitomer, Adina, Sarah Shugars, Ryan J. Gallagher, \textbf{Stefan McCabe}, and Brooke Foucault Welles. 2023. ``The Speech We Miss: How Keyword Based Data Collection Obscures Participation in Online Election Discourse.''  \textit{Computational Communication Research} 5 (1). doi:\href{https://doi.org/10.5117/CCR2023.1.11.GITO}{10.5117/CCR2023.1.11.GITO}\vspace{2mm}
\end{hangparas}

\subsection{2022}
\begin{hangparas}{.25in}{1}
Green, Jon, William Hobbs, \textbf{Stefan McCabe}, and David Lazer. 2022. “Online Engagement with 2020 Election Misinformation and Turnout in the 2021 Georgia Runoff Election.” \textit{Proceedings of the National Academy of Sciences} 119 (34): e2115900119. doi:\href{https://doi.org/10.1073/pnas.2115900119}{10.1073/pnas.2115900119}.
\vspace{2mm}

Klein, Brennan, Nicholas Generous, Matteo Chinazzi, Zarana Bhadricha, Rishab Gunashekar, Preeti Kori, Bodian Li, \textbf{Stefan McCabe}, Jon Green, David Lazer, Christopher R. Marsicano, Samuel V. Scarpino, and Alessandro Vespignani. 2022. \textit{PLOS Digital Health}. ``Higher education responses to COVID-19 in the United States: Evidence for the impacts of university policy.'' doi:\href{https://doi.org/10.1371/journal.pdig.0000065}{10.1371/journal.pdig.0000065}.
\vspace{2mm}
\end{hangparas}


\subsection{2021}
\begin{hangparas}{.25in}{1}
Hughes, Adam G.,\textsuperscript{\textdagger} \textbf{Stefan D. McCabe},\textsuperscript{\textdagger} William R. Hobbs, Emma Remy, Sono Shah, and David M.~J. Lazer. 2021. ``Using Administrative Records and Survey Data to Construct Samples of Tweeters and Tweets.'' \textit{Public Opinion Quarterly} 85 (S1): 323--346. doi:\href{https://doi.org/10.1093/poq/nfab020}{10.1093/poq/nfab020}
\vspace{-1mm}

\textbf{McCabe, Stefan}, Leo Torres, Timothy LaRock, Syed Arefinul Haque, Chia-Hung Yang, Harrison Hartle, and Brennan Klein. 2021. ``netrd: A Library for Network Reconstruction and Graph Distances.'' \textit{Journal of Open Source Software} 6 (62): 2990. doi:\href{https://doi.org/10.21105/joss.02990}{10.21105/joss.02990} arXiv:\href{https://arxiv.org/abs/2010.16019}{2010.16019}
\vspace{-1mm}

Shugars, Sarah, Adina Gitomer, \textbf{Stefan D. McCabe}, Ryan J. Gallagher, Kenneth Joseph, Nir Grinberg, Larissa Doroshenko, Brooke Foucult Welles, and David Lazer. 2021. ``Pandemics, Protests, and Publics: Demographic Activity and Engagement on Twitter in 2020.'' \textit{Journal of Quantitative Description: Digital Media} 1. doi:\href{https://doi.org/10.51685/jqd.2021.002}{10.51685/jqd.2021.002}
\vspace{2mm}
\end{hangparas}

\subsection{2020}
\begin{hangparas}{.25in}{1}
  Hartle, Harrison, Brennan Klein, \textbf{Stefan McCabe}, Alexander Daniels, Guillaume St-Onge, Charles Murphy, and Laurent Hébert-Dufresne. 2020. ``Network Comparison and the Within-Ensemble Graph Distance.'' \textit{Proceedings of the Royal Society A} 476 (2243): 20190744. doi:\href{https://doi.org/10.1098/rspa.2019.0744}{10.1098/rspa.2019.0744}. arXiv:\href{https://arxiv.org/abs/2008.02415}{2008.02415} \vspace{2mm}
\end{hangparas}

% section heading is currently at the bottom of p1 - using a clearpage to reset it. remove as needed
% \clearpage

\section{working papers}
\subsection*{} % force placement of section heading - doesn't play nice
               % with hangingparas otherwise
\vspace{-6mm} % ignore phantom subsection* when placing first paper
\begin{hangparas}{.25in}{1}

Green, Jon,\textsuperscript{\textdagger} \textbf{Stefan McCabe},\textsuperscript{\textdagger} Sarah Shugars, Hanyu Chwe, Luke Horgan, Shuyang Cao and David Lazer. Under review. ``Curation Bubbles.'' \href{https://osf.io/udfaz/}{https://osf.io/udfaz/} \vspace{2mm}

\textbf{McCabe, Stefan}, and Matthew Hindman. In preparation. ``Reconstructing Public Activity on Digital Platforms.'' \vspace{2mm}

Yang, Yunkang, \textbf{Stefan McCabe}, and Matthew Hindman. In preparation. ``Russian Propaganda on Facebook: Topic Coverage and User Engagement with RT and Sputnik Over Six Years.'' \vspace{2mm}

Thompson, Andrew Ifedapo, \textbf{Stefan McCabe}, and Babak Bahador. Under review. ``The Long Shadow of the Civil War: The Recurrent Historical Centrality of Anti-Black Political Threat in Eroding Public Support for American Democracy.'' \href{https://osf.io/fp35j/}{https://osf.io/fp35j/} \vspace{2mm}

Busby, Ethan, Andrew Ifedapo Thompson, and \textbf{Stefan McCabe}. Under review. ``Party-Ideology Sorting in the United States: Correlates and Consequences.'' \vspace{2mm}

Thompson, Andrew Ifedapo, and \textbf{Stefan McCabe}. Under review. ``Racial Innumeracy: Reorienting the Interpretation of Racial Demographic Change in the Mass Public''  \vspace{2mm}

Thompson, Andrew Ifedapo, Malia Bowers, and \textbf{Stefan McCabe}. Under review. ``White Supremacy, Democrats, and Anti-Abortion Support.'' \href{https://osf.io/3y4q9/}{https://osf.io/3y4q9/} \vspace{2mm}

Thompson, Andrew Ifedapo, and \textbf{Stefan McCabe}. In preparation. ``Black Entry, White Flight: Democratic Erosion and Causal Determinants of Insurrectionist Sentiment.''  \vspace{2mm}


%\textbf{McCabe, Stefan}, Jon Green, Allison Wan, and David Lazer. In
%preparation. ``New Tweetscores.''\vspace{2mm}

\textbf{McCabe, Stefan}, Jon Green, Pranav Goel and David Lazer. Under review. ``How Representative is Online Representation? A Descriptive Analysis of Who Follows Their Own Member of Congress on Twitter.''\vspace{2mm}

Esterling, Kevin M.,\textsuperscript{\textdagger} \textbf{Stefan D. McCabe},\textsuperscript{\textdagger} Diogo Ferrari, Jon Green and David M. J. Lazer. In preparation. ``Deplatforming Right-Wing Extremists on Twitter Following the January 6 Insurrection.''\vspace{2mm}


%Klein, Brennan, Harrison Hartle, Leo Torres, \textbf{Stefan D. McCabe},
%Chia-Hung Yang, Timothy LaRock, David Saffo, et al. In preparation. ``Comparing
%Methods for Reconstructing Networks from Time Series Data by Comparing Methods
%for Measuring Network Similarity.'' \vspace{2mm}

%\textbf{McCabe, Stefan D.}, David Lazer, William Minozzi, Michael A. Neblo, and
%Brian Rubineau. In preparation. ``Timescales of Social Influence.'' \vspace{2mm}

\end{hangparas}

\section{invited talks}
\subsection{2022}
\begin{hangparas}{.25in}{1}
``Using Administrative Records and Survey Data to Construct Samples of Tweeters and Tweets,'' oral presentation, DC-AAPOR Webinar. (with Adam G. Hughes, William R. Hobbs, Emma Remy, Sono Shah, David Lazer) \vspace{2mm}
\end{hangparas}

\vspace{2mm}
\section{conference talks}

\subsection{2022}
\begin{hangparas}{.25in}{1}
``Deplatforming Right-Wing Extremists on Twitter Following the January 6 Insurrection,'' oral presentation, Annual Meeting of the American Political Science Association, online conference. (with Kevin Esterling, Diogo Ferrari, Jon Green, David Lazer)
\vspace{2mm}

``New Tweetscores, or, Did Donald Trump Break Tweetscores?,'' oral presentation, Political Networks Conference, online conference. (with Jon Green, Allison Wan, David Lazer)
\vspace{2mm}

``Despair or Defiance? Assessing the Turnout Effects of Election Misinformation,'' oral presentation, Politics and Computational Social Science Conference, Cambridge, MA. (with Jon Green, Will Hobbs, David Lazer)
\vspace{2mm}

``New Tweetscores, or, Did Donald Trump Break Tweetscores?,'' oral presentation, Annual Meeting of the Midwestern Political Science Association, Chicago, IL. (with Jon Green, Allison Wan, David Lazer)
\vspace{2mm}
\end{hangparas}

\subsection{2021}
\begin{hangparas}{.25in}{1}
``Despair or Defiance? Assessing the Turnout Effects of Election Misinformation,'' oral presentation, Annual Meeting of the American Political Science Association, online conference. (with Jon Green, Will Hobbs, David Lazer)
\vspace{2mm}

``Curation Bubbles,'' oral presentation, Politics and Computational Social Science, online conference. (with Jon Green, Sarah Shugars, John Harrington, Hanyu Chwe, Shuyang Cao, David Lazer)
\vspace{2mm}

``How Representative are the (Online) Represented?,'' oral presentation, Networks 2021, online conference. (with Jon Green, Pranav Goel, David Lazer)
\vspace{2mm}

``How Representative are the (Online) Represented?,'' oral presentation, Political Networks Conference, online conference. (with Jon Green, Pranav Goel, David Lazer)
\vspace{2mm}

``Curation Bubbles,'' oral presentation, Annual Meeting of the Midwestern Political Science Association, online conference. (with Jon Green, Sarah Shugars, John Harrington, David Lazer)
\vspace{2mm}
\end{hangparas}

\subsection{2020}
\begin{hangparas}{.25in}{1}
``Twitter is Real Life (for Journalists),'' oral presentation, Politics and Computational Social Science, online conference. (with David Rothschild)
\vspace{2mm}

``A Vocal Minority: Assessing the Representativeness of Tweeters and Tweets,'' oral presentation, International Conference on Computational Social Science, online conference. (with Adam G. Hughes, William R. Hobbs, Emma Remy, Sono Shah, David Lazer)
\vspace{2mm}
\end{hangparas}

\subsection{2019}
\begin{hangparas}{.25in}{1}
``Time Scales of Social Influence,'' oral presentation, Annual Meeting of the Midwestern Political Science Assocation, Chicago, IL. (with David Lazer, William Minozzi, Michael Neblo, Brian Rubineau)
\vspace{2mm}

``Time Scales of Social Influence,'' oral presentation, Political Networks Conference, Durham, NC. (with David Lazer, William Minozzi, Michael Neblo, Brian Rubineau)
\vspace{2mm}

``Local Edge Perturbations as a Measure for Community Peristence in Complex Networks,'' poster, NetSci, Burlington, VT. (with Brennan Klein)
\vspace{2mm}

``Time Scales of Social Influence,'' oral presentation, Sunbelt Conference, Montréal. (with David Lazer, William Minozzi, Michael Neblo, Brian Rubineau)
\vspace{2mm}

``Time Scales of Social Influence,'' oral presentation, Annual Meeting of the American Political Science Assocation, Washington DC. (with David Lazer, William Minozzi, Michael Neblo, Brian Rubineau)
\vspace{2mm}
\end{hangparas}

\vspace{2mm}
\section{courses taught}
\subsection{2020}
\begin{hangparas}{.25in}{1}
``Complex Networks and Applications.'' Fall 2020. (Graduate course, co-instructor)
\end{hangparas}
\vspace{1mm}

\subsection{2019}
\begin{hangparas}{.25in}{1}
``Programming with Data: Social Science Practicum.'' Fall 2019. (Undergraduate course, instructor) \vspace{2mm}
\end{hangparas}


 \section{service}
 Reviewer for \textit{Proceedings of the National Academy of Sciences}, \textit{Connections}, \textit{Journal of Online Trust and Safety}, \textit{Journal of Quantitative Description: Digital Media}, \textit{Online Social Networks and Media}.

 Program Committee, Politics and Computational Social Science conference, 2018--2019, 2022.

 Treasurer, Network Science Institute Graduate Student Association, 2019--2021.

 Student Representative, Network Science Institute Graduate Admission Council, 2019.

 Co-organizer, Society of Young Network Scientists pre-conference event, NetSci, Burlington, VT, 2019.

\end{document}
